---
title: "linear model from Web"
author: "Kathleen Castro"
date: "Spring,  2023"
output:
   html_document:
         toc: true
         toc_depth: 5
        
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Read about the data from the website where it is staged.  Then form three regression models; Model1 is SIMS~ARM, Model2 is SIMS~GRIP, and Model3 is SIMS~ARM+GRIP. For each model find a 95% prediction interval of SIMS given a value of 94  for GRIP and 88 for ARM. Compare Model1 with Model3 using anova. Write it up in a markdown document, push the project up to your github account and submit it back to canvas as link. 

 


```{r include=FALSE}
require(tidyverse)
require(tigerstats)
require(rgl)
require(knitr)

```

```{r}
data <- read.csv(file="https://onlinestatbook.com/case_studies_rvls/physical_strength/data.txt",sep="",header=TRUE)  

```

## Model 1 SIM~ARMS

### scatterplot
```{r}
basicNN <- ggplot(data,aes(y=SIMS,x=ARM))
```
```{r}
basicNN + geom_point() + ggtitle("SIMS vs ARMS") + theme(plot.title = element_text(hjust = 0.5, size = 20))
```
  
The data analysed above show the results of a simulation giving data on the strength of workers arms. The expected strength ranges from 50 to 100 within the workers. 

### Numerical results
```{r}
cor(SIMS~ARM,data=data)
```
  
The data presented above explains that the larger the number becomes, the more correlated the results end up being. Since the number is approaching 1, we can stipulate that there will be a small correspondence.

### Inferential  (Build model.1)
```{r}
model.1 <- lm(SIMS~ARM,data=data)
summary.lm(model.1)
```
  
The equation for the line provided by the inferential data is : SIMS=0.054563xARM=-4.095160. This equation proves that the line is increasing from the bottom to the top.
#### Predict at target point

```{r}
tgtpoint=data.frame(ARM=88, GRIP=94)

predict(model.1, tgtpoint, interval= c("prediction"))
```
  
looking at the table we can see that the predicted target plot is at 0.7063836; however about every 95% of the time, our results will range from -1.726209 to 3.138977.



#### scatterplot with model fit
```{r}
basicNN + geom_point() + ggtitle ("SIMS vs ARM") + theme(plot.title = element_text(hjust = 0.5, size = 20)) + geom_smooth(method=lm)
```   
  
The data above gives us the best fit line to help us collect all out data and see the similarities for each data point.

## Model 2 SIM~GRIP

### Now add in scatterplot

```{r}
basicGRIP <- ggplot(data,aes(y=SIMS,x=GRIP))

basicGRIP + geom_point() + ggtitle ("SIMS vs GRIP") + theme(plot.title = element_text(hjust = 0.5, size = 20))
```  


### Numerical results 
```{r}
cor(SIMS~GRIP,data=data)
```
  
Comparing the given amount of SIMS vs GRIP, 0.6398458, with our other given amount found from SIMS vs ARMS, 0.6860073, we can see a small difference between the two differing sides. This data shows how the SIMS vs ARMS model gives a more accurate reading compared to the SIMS vs GRIP model.

### Inferential  (Build model.2)
```{r}
model.2 <- lm(SIMS~GRIP,data=data)
summary.lm(model.1)
```  
  
The data provided above gives us the equation: SIMS= 0.045463x GRIP= -4.809675 for the line of best fit. These coefficients prove that the slope will be increasing.

#### predict model.2 at target point
```{r}
predict(model.2, tgtpoint, interval= c("prediction"))
```
  
The table shows us the value for our best fit line which is -0.5361543. While this amount is given, 95% of the time we will have our result range from -3.107961 to 2.035652.

#### now add the model fit to our plot for model.2
```{r}
basicGRIP + geom_point() + ggtitle ("SIMS vs GRIP") + theme(plot.title = element_text(hjust = 0.5, size = 20)) + geom_smooth(method=lm)
```    
  
The graph presented above gives us the line of best fit which points out that our data carries the most accurate info in SIMS vs GRIP.
## Model 3 SIM~ARM+GRIP

### Numerical results (cor)

```{r}
cor(SIMS~ARM+GRIP,data=data)
```
  
The value provided shows we have a 0.7326545 correlation for SIMS vs ARMS+GRIP. This value shows a higher difference when looking at both SIMS vs ARMS and SIMS vs GRIP. This has become the most accurate model when looking at both data sets together rather than separate.
  
### Inferential  (Build 2-dimentional model.3)
```{r}
model.3 <- lm(SIMS~ARM+GRIP,data=data)
summary.lm(model.3)
``` 
  
The data provided above gives us the equation: SIMS= 0.037311xARM + 0.024470xGRIP -5.433871 for the best fit line.

#### predict model.3 at target point
```{r}
predict(model.3, tgtpoint, interval= c("prediction"))
```  
  
This table shows us the value 0.1496476 is the target point for the SIMS vs ARM+GRIP. In the 95% of the time, we will be obtaining the values -2.132373 to 2.431668.

## Comparing nested models ANOVA Test

### Model.1 vs Model.3
```{r}
anova(model.1,model.3)
```
  
The model 1.3 shows more accurate data compared to model 1.1. The two models share no big differences based on the data provided above. The difference outcome comes out to 0.000004994% chance. We can also see a 145 degree of freedom for the model 1.1 and a 144 degree for the model 1.3. The plots with ARM+GRIP gives a more accruate reading by 29.45 points.

### Model.2 vs Model.3
```{r}
anova(model.2,model.3)
```
  
In this data table, we can observe how model 1.3 has proven to be more accurate compared to model 1.2. There are no difference between the two models leaving a 0.00000000001495% chance of ending up with the same results. Looking at the degree of freedom, we can see that 1.2 model had 145 while model 1.3 had a 144. The difference of 54.639 in errors will make model 1.3 more accruate in total.

## Informally compare Model.1 with model.2

