---
title: "linear model from Web"
author: "Kathleen Castro"
date: "Spring,  2023"
output:
   html_document:
         toc: true
         toc_depth: 5
        
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Read about the data from the website where it is staged.  Then form three regression models; Model1 is SIMS~ARM, Model2 is SIMS~GRIP, and Model3 is SIMS~ARM+GRIP. For each model find a 95% prediction interval of SIMS given a value of 94  for GRIP and 88 for ARM. Compare Model1 with Model3 using anova. Write it up in a markdown document, push the project up to your github account and submit it back to canvas as link. 

 


```{r include=FALSE}
require(tidyverse)
require(tigerstats)
require(rgl)
require(knitr)

```

```{r}
data <- read.csv(file="https://onlinestatbook.com/case_studies_rvls/physical_strength/data.txt",sep="",header=TRUE)  

```

## Model 1 SIM~ARMS

### scatterplot
```{r}
basicNN <- ggplot(data,aes(y=SIMS,x=ARM))
```
```{r}
basicNN + geom_point() + ggtitle("SIMS vs ARMS") + theme(plot.title = element_text(hjust = 0.5, size = 20))
```
  
The data analysed above show the results of a simulation giving data on the strength of workers arms. The expected strength ranges from 50 to 100 within the workers. 

### Numerical results
```{r}
cor(SIMS~ARM,data=data)
```
  
The data presented above explains that the larger the number becomes, the more correlated the results end up being. Since the number is approaching 1, we can stipulate that there will be a small correspondence.

### Inferential  (Build model.1)
```{r}
model.1 <- lm(SIMS~ARM,data=data)
summary.lm(model.1)
```
  
The equation for the line provided by the inferential data is : SIMS=0.054563xARM=-4.095160. This equation proves that the line is increasing from the bottom to the top.
#### Predict at target point

```{r}
tgtpoint=data.frame(ARM=88, GRIP=94)

predict(model.1, tgtpoint, interval= c("prediction"))
```
  
looking at the table we can see that the predicted target plot is at 0.7063836; however about every 95% of the time, our results will range from -1.726209 to 3.138977.



#### scatterplot with model fit
```{r}
basicNN + geom_point() + ggtitle ("SIMS vs ARM") + theme(plot.title = element_text(hjust = 0.5, size = 20)) + geom_smooth(method=lm)
```   
  
The data above gives us the best fit line to help us collect all out data and see the similarities for each data point.

## Model 2 SIM~GRIP

### Now add in scatterplot

```{r}
basicGRIP <- ggplot(data,aes(y=SIMS,x=GRIP))

basicGRIP + geom_point() + ggtitle ("SIMS vs GRIP") + theme(plot.title = element_text(hjust = 0.5, size = 20))
```  


### Numerical results 
```{r}
cor(SIMS~GRIP,data=data)
```
  
Comparing the given amount of SIMS vs GRIP, 0.6398458, with our other given amount found from SIMS vs ARMS, 0.6860073, we can see a small difference between the two differing sides. This data shows how the SIMS vs ARMS model gives a more accurate reading compared to the SIMS vs GRIP model.

### Inferential  (Build model.2)
```{r}
model.2 <- lm(SIMS~GRIP,data=data)
summary.lm(model.1)
```  
  
The data provided above gives us the equation: SIMS= 0.045463x GRIP= -4.809675 for the line of best fit. These coefficients prove that the slope will be increasing.

#### predict model.2 at target point
```{r}
predict(model.2, tgtpoint, interval= c("prediction"))
```
  
The table shows us the value for our best fit line which is -0.5361543. While this amount is given, 95% of the time we will have our result range from -3.107961 to 2.035652.

#### now add the model fit to our plot for model.2
```{r}
basicGRIP + geom_point() + ggtitle ("SIMS vs GRIP") + theme(plot.title = element_text(hjust = 0.5, size = 20)) + geom_smooth(method=lm)
```    
  
The graph presented above gives us the line of best fit which points out that our data carries the most accurate info in SIMS vs GRIP.
## Model 3 SIM~ARM+GRIP

### Numerical results (cor)

`
  
### Inferential  (Build 2-dimentional model.3)

#### predict model.3 at target point
  

## Comparing nested models ANOVA Test

### Model.1 vs Model.3
### Model.2 vs Model.3

## Informally compare Model.1 with model.2

